\chapter{CONCLUSION AND FUTURE WORK}
    \section{Conclusion}
    Lessons learned by undertaking this project
    \begin{itemize}
        \item Writing the report following the standard methods was another learning outcome. 
        \item Obtain knowledge in programming with Nodejs and MongoDB.
        \item From the beginning, requirement gathering to the deployment of the system was not a smooth task. It helped all members to learn to cooperate with people and to manage work and time 
    \end{itemize}
    \section{Future Work}
    As technology evolves and guest expectations change, continuous improvement of our Hotel Management System (HMS) is essential. Here are several areas of future work and potential improvements that can be integrated into the HMS to ensure it remains at the forefront of hotel management technology:
    \begin{itemize}
        \item \textbf{Expanded System Scope:} The expanded scope will encompass the following aspects:
        \begin{itemize}
            \item Incorporating features for managing events, conferences, and banquets, including booking spaces, scheduling, and coordinating catering and equipment.
            \item Managing appointments, staff, inventory, and customer preferences for spa and wellness services.
            \item Streamlining the management of recreational facilities like gyms, pools, and activity centers.
        \end{itemize}
        \item \textbf{Chatbots and Virtual Assistants:} Advanced chatbots and virtual assistants using natural language processing can provide 24/7 customer service for common inquiries and requests, reducing the workload on staff and improving guest satisfaction.
    \end{itemize}