\chapter{INTRODUCTION}
    \section{Introduction}
    In the fast-paced world of hospitality, efficient management and seamless guest experiences are paramount. The Hotel Management System (HMS) is a software solution designed to computerize how the hotel operates, enhancing guest satisfaction, streamlining administrative tasks, and maximizing overall productivity. This innovative technology integrates various aspects of hotel operations into a centralized platform, offering hoteliers powerful tools to optimize their services.
    \section{System Description}
    Our Hotel Management System (HMS) is an integrated software platform designed to streamline the operational efficiency of hotel and services. 
    \begin{itemize}
        \item \textbf{Room Booking and Reservations:} The HMS offers a room booking and reservation module that allows users to easily check room availability, book rooms, and manage reservations. 
        \item \textbf{Front Desk Operations:} The front desk module streamlines daily operations such as room assignments.
        \item \textbf{In-Room Dining:} Guests can view menu items, and place orders through a receptionist. Meal charges are seamlessly integrated into the guest’s overall billing.
        \item \textbf{Airport Transfer Services:} Guests can book airport transfer services, specifying details such as pickup and drop-off location, specific time, and preferred vehicle type. Similar to the meal service, airport transfer charges are integrated into the guest's bill.
        \item \textbf{Customer service:} Helps in managing customer relationships through feedback collection.
    \end{itemize}
    \section{Topic Objectives}
    The main objective of this system is to improve efficiency, reduce the overall manual workload of the hotel and provide suitable technical and profitable solutions for current problems such as time-consuming, heavy calculations. 
    
    \textbf{Given below are the points that mention what are the objectives achieved by the project:}
    \begin{itemize}
        \item Provide a system that helps check the room availability, make the relevant reservations efficiently, and replace the reservation book.
        \item Automate some possible current work being done manually in the hotel. Ability to check the current situation of the hotel with less effort and less time with high efficiency.
    \end{itemize}
    \section{Topic Scope}
    Our Hotel Management System will have 4 end users: Customer, Receptionist, Accountant and Hotel Manager. Customers will able to check for room availability, see the room information, and book some accompanying services. Receptionists will have access to check for room’s availability to book for customer, assist hotel guests with the check-in and check-out processes, including handling reservations and payments, send customer feedback to the management. Accountants can view the hotel's revenue to make reports for management as well as resolve errors easily. Manager will able to update room information such as cost and category change the guest's booking schedule upon request.
    \vspace{5mm} %5mm vertical space
    
    The main goal of this web-based is to simplify every day process of hotel. Day to day Hotels are increasing and they need to automate to provide customer ease of access. It will be able to take care of services to customer in a quick manner. This automation will be able to replace the drawbacks of large customer information physical files which were difficult to handle. 
    \section{Limitation }
    \begin{itemize}
        \item The system does not support multiple room bookings.
        \item The system primarily focuses on basic guest interactions and lacks features for direct guest communication, and advanced guest services (like spa booking, event participation, or personalized tour planning).
        \item  There are no features related to staff management, or scheduling within the system.
        \item The system does not provide advanced analytics or customizable reporting features that can provide deeper insights into hotel operations.
        \item The system lacks functionality for managing and tracking maintenance and repairs of hotel properties.
        \item The system does not include features for user roles such as housekeepers or security staff, limiting their direct involvement in its operations.
    \end{itemize}
    \section{Report Structure}
    The report is divided into 5 chapters:\\
        \indent• Chapter 1: Introduction\\
        \indent Introducing the topic, System description, Topic Objectives and Scope, Limitation, Topic contribution and Report structure.\\
        \indent• Chapter 2: System analysis and design\\
        \indent Including Functional requirements, Non-functional requirements, Use-Case diagram, Data flow diagram (DFD), Entity relationship diagram (ERD) and Physical database design.\\
        \indent• Chapter 3: System implementation\\
        \indent Describing used technologies in website to implement the system and system architecture. \\
        \indent• Chapter 4: Demo System \\
        \indent Including system scenarios and demonstrating the system through screenshots. \\
        \indent• Chapter 5: Conclusion and future work\\
        \indent• References \\
        \indent• List of Requirement Questions