\chapter{SYSTEM IMPLEMENTATION}
    \section{Technical Stack}
    In the development of our Hotel Management System (HMS), we have chosen a robust and versatile technology stack that ensures both efficiency and scalability. Our selection encompasses both front-end and back-end technologies, each playing a crucial role in creating a seamless user experience and robust backend functionality. \\
    \textbf{* Front-end Technologies:}
    \begin{enumerate}
        \item EJS (Embedded JavaScript templating): We use EJS as our templating language to generate HTML markup with plain JavaScript. It provides an easy-to-use, flexible solution for rendering server-side data into HTML, ensuring dynamic content delivery that's integral for interactive user interfaces.
        \item CSS: Cascading Style Sheets (CSS) are employed for styling the web pages. With CSS, we ensure that the user interface is not only functional but also aesthetically pleasing, providing an engaging user experience.
        \item JavaScript: As the scripting language for the Web, JavaScript is used to create interactive and dynamic user interfaces. It enables us to implement complex features such as real-time updates, interactive forms, and other user-centric functionalities.
        \item jQuery: jQuery simplifies HTML DOM tree traversal and manipulation, event handling, and animation, making it easier and quicker to develop JavaScript-based functionalities. It's particularly useful in enhancing the interactivity and responsiveness of the HMS.
        \item Bootstrap: For responsive design, we integrate Bootstrap, a powerful front-end framework. Bootstrap's ready-to-use components and responsive grid system allow our HMS to be mobile-friendly and adaptable across various devices and screen sizes.
    \end{enumerate}
    \textbf{* Back-end Technologies:}
    \begin{enumerate}
        \item Node.js: At the core of our back-end development is Node.js, a JavaScript runtime built on Chrome's V8 JavaScript engine. Node.js enables us to build fast and scalable network applications, perfectly suited for handling the extensive data processing required in hotel management systems.
        \item Express.js: A minimal and flexible Node.js web application framework that provides a robust set of features for web and mobile applications.
        \item Passport.js: A middleware for Node.js that simplifies the process of handling user authentication.
        \item MongoDB: As our database solution, we use MongoDB, a NoSQL database known for its high performance, high availability, and easy scalability. Its flexible data model is ideal for handling diverse data types that a hotel management system entails.
        \item Mongoose: To streamline working with MongoDB, Mongoose, an Object Data Modeling (ODM) library, is utilized. Mongoose provides a straightforward schema-based solution to model application data. It includes built-in type casting, validation, query building, and business logic hooks.
        
    \end{enumerate}
    \section{System Architecture}
    